---
title: "lab4_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab4_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(lab4)
data("iris")
```

# Introduction

This package implement a class to create a linear regression model. You can see the details in [Linear Regression](https://en.wikipedia.org/wiki/Linear_regression){.uri}.

# Initialize

To initialize the class, 2 parameters required, one is formula in the type of "language", another is data in the type of "matrix". Take the iris dataset for example:

```{r initialization example}
object <- linreg(formula = Petal.Length ~ Species ,data = iris)

```

After running this code chunk, you initialize an instance of the model.

# Call Core Functions

There are few core functions for the class, you can call them after initialization:

## print()

Function print() implements printing the coefficients matrix of regression.

```{r print call example}
object$print()
```

## plot()

Function plot() implements plots named "Residuals vs Fitted" and "Scale-Location" Parameter: which = 1 "Residuals vs Fitted" displayed which = 3 "Scale-Location" displayed

```{r plot example}
object$plot(which = 1)
object$plot(which = 3)

```

## resid()

Function resid() returns the residuals.

```{r resid example}
object$resid()
```

## pred()

Function pred() returns the predicted value of y.

```{r pred example}
object$pred()
# 
```

## coef()

Function coef() returns the coefficients matrix.

```{r coef example}
object$coef()
```

## summary()

Function summary() prints a similar printout as printed for lm objects, presenting the coeffcients with their standard error, t-value and p-value as well as the estimate of residual variance and the degrees of freedom in the model.

```{r summary example}
object$summary()
```
