---
title: "Ridge Regression Usage"
author: "Cui Qingxuan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Ridge Regression Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Introduction of Ridge Regression Function

This rmd file is used to demostrate how to use customised ridge regression model via example.
There are some specification about its structure. The definition of ridge regression model implemented in the definition of linreg class as a function. However, we need to invoke it after initialization. Here is example.
```{r}
library(lab4)
```

## Initialize the class with parameter named "ridge"

```{r}
example <- linreg$new(Petal.Length~Species, data = iris, model = "ridge")
```

## Invoke the function to calculate the coefficients

You can set the method as 1 or 2, the former one represent linear algebra method, and the later one for QR decomposition method.
```{r}
example$ridgereg(lambda = 0.2, method = 1)
```
After invocation, both the coefficients and fitted value have been calculated, but you can still directly invoke the function pred(), to predict.
```{r}
example$print()
```
Of course you can invoke print to check that.

